\section*{Appendix A: kickstarter campaign}
\textbf{Goal:} the target of our company is to reach 50’000€ with a Kickstarter campaign selling our products with a remarkable discount to the future price. 

\textbf{Money on video making:} -200€ 

\textbf{Stock price of the bottle:} 55€ (40€ food + 25€ water) 

\textbf{Price list:}
\begin{itemize}
    \item \textbf{5€ (∞) support}
    Thank you for cheering us on! Your support means so much to us and you'll be among the first to hear about any and all developments with BottAll.
    \item \textbf{33€ (400) limited complete pack (save 40\%)}
    Be the first to own a BottAll complete pack in any of our available Colours, Style or choose a Mix n Match. 

    \item \textbf{17€ (200) limited only-water pack (save 32\%) }
    Be the first to own a BottAll water pack in any of our available Colours, Style or choose a Mix n Match. 
    \item \textbf{29€ (200) limited only food (save 29\%) }
    Be the first to own a BottAll food container pack in any of our available Colours, Style or choose a Mix n Match. 
    \item \textbf{38€ (500) limited complete pack (save 31\%)}
    Maybe it is not too late to have a special discount. 
    \item \textbf{45€ (∞) special Kickstarter complete pack price (save 19\%) }
    Be one of the first to own a BottAll, you will be able to special price for our Kickstarter campaign. 
    \item \textbf{60€ (200) x2 limited Kickstarter complete pack price (save 45\%)} 
    Be one of the first to own a BottAll, you will be able to special price for our Kickstarter campaign. 
    \item \textbf{77€ (∞) x2 special Kickstarter complete pack price (save 30\%)}
    Be one of the first to own a BottAll, you will be able to special price for our Kickstarter campaign. 
    \item \textbf{100€ (200) x3 limited Kickstarter complete pack price (save 40\%)}
    Be one of the first to own a BottAll, you will be able to special price for our Kickstarter campaign 
    \item \textbf{300€ (200) x10 limited Kickstarter complete pack price (save 45\%)}
    Be one of the first to own a BottAll, you will be able to special price for our Kickstarter campaign. 
    \item \textbf{400€ (∞) x10 special Kickstarter complete pack price (save 28\%)} 
    Be one of the first to own a BottAll, you will be able to special price for our Kickstarter campaign. 
\end{itemize}



